---
title: "Exploring Corruption Perceptions Index and Human Development Index"
author: "Rohit Dixit"
date: "8/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
The purpose of this project is data exploration and plotting. Not effiecient coding. 

#Loading libraries & Data
```{r}
library(ggplot2)
library(data.table)
library(ggthemes)
df <- fread('Economist_Assignment_Data.csv',drop=1)
```

## Exploring data
```{r}
head(df)
```

## Plot of CPI & HDI plotted by Region
```{r}
pl <- ggplot(df,aes(x=CPI,y=HDI,color=Region)) + geom_point()
pl
```

## Adding a trend line to see the trend
```{r}
pl <- ggplot(df,aes(x=CPI,y=HDI,color=Region)) + geom_point(size=4,shape=1)
pl + geom_smooth(aes(group=1))
pl
```

## Editing the trend line and adding country labels
```{r}
pl2 <- pl + geom_smooth(aes(group=1),method ='lm',formula = y~log(x),se=FALSE,color='red')
pl2 + geom_text(aes(label=Country))
```

## De-cluttering the plot by manually selecting a subset of countries to select
```{r}
pointsToLabel <- c("Russia", "Venezuela", "Iraq", "Myanmar", "Sudan",
                   "Afghanistan", "Congo", "Greece", "Argentina", "Brazil",
                   "India", "Italy", "China", "South Africa", "Spane",
                   "Botswana", "Cape Verde", "Bhutan", "Rwanda", "France",
                   "United States", "Germany", "Britain", "Barbados", "Norway", "Japan",
                   "New Zealand", "Singapore")

pl3 <- pl2 + geom_text(aes(label = Country), color = "gray20", 
                data = subset(df, Country %in% pointsToLabel),check_overlap = TRUE)

pl3
```

## Adding axis labels to the plot
```{r}
pl4 <- pl3 + theme_bw() 
pl4
pl5 <- pl4 + scale_x_continuous(name = "Corruption Perceptions Index, 2011 (10=least corrupt)",
                     limits = c(.9, 10.5),breaks=1:10) 
pl5
pl6 <- pl5 + scale_y_continuous(name = "Human Development Index, 2011 (1=Best)",
                     limits = c(0.2, 1.0))
pl6
```

## Adding Title
```{r}
pl6 + ggtitle("Corruption and Human development")
pl6 + theme_economist_white()
```

## Conclusion
Looking at the plot the trend line shows a liner relationship exist between Corruption Percentage Index and Human Development Index. The better CPI the better HDI or vice-versa. The goal of the project was to explore the data and see if any meaningful relationships are present in the data.